% Copyright 2013 Christophe-Marie Duquesne <chmd@chmd.fr>
% Copyright 2014 Mark Szepieniec <http://github.com/mszep>
% 
% ConText style for making a resume with pandoc. Inspired by moderncv.
% 
% This CSS document is delivered to you under the CC BY-SA 3.0 License.
% https://creativecommons.org/licenses/by-sa/3.0/deed.en_US

\startmode[*mkii]
  \enableregime[utf-8]  
  \setupcolors[state=start]
\stopmode

\setupcolor[hex]
\definecolor[titlegrey][h=757575]
\definecolor[sectioncolor][h=397249]
\definecolor[rulecolor][h=9cb770]

% Enable hyperlinks
\setupinteraction[state=start, color=sectioncolor]

\setuppapersize [A4][A4]
\setuplayout    [width=middle, height=middle,
                 backspace=20mm, cutspace=0mm,
                 topspace=10mm, bottomspace=20mm,
                 header=0mm, footer=0mm]

%\setuppagenumbering[location={footer,center}]

\setupbodyfont[11pt, helvetica]

\setupwhitespace[medium]

\setupblackrules[width=31mm, color=rulecolor]

\setuphead[chapter]      [style=\tfd]
\setuphead[section]      [style=\tfd\bf, color=titlegrey, align=middle]
\setuphead[subsection]   [style=\tfb\bf, color=sectioncolor, align=right,
                          before={\leavevmode\blackrule\hspace}]
\setuphead[subsubsection][style=\bf]

\setuphead[chapter, section, subsection, subsubsection][number=no]

%\setupdescriptions[width=10mm]

\definedescription
  [description]
  [headstyle=bold, style=normal,
   location=hanging, width=18mm, distance=14mm, margin=0cm]

\setupitemize[autointro, packed]    % prevent orphan list intro
\setupitemize[indentnext=no]

\setupfloat[figure][default={here,nonumber}]
\setupfloat[table][default={here,nonumber}]

\setuptables[textwidth=max, HL=none]

\setupthinrules[width=15em] % width of horizontal rules

\setupdelimitedtext
  [blockquote]
  [before={\setupalign[middle]},
   indentnext=no,
  ]


\starttext

\section[stefanos-georgiou]{Stefanos Georgiou}

\thinrule

\startblockquote
{\bf Contact details}: stefanos1316@gmail.com, sgeorgiou@aueb.gr,
sgeorgiou@singularlogic.eu
\stopblockquote

\startblockquote
{\bf About me}: I am passionated with coding, performing experimental
studies, learning and combining new technologies. On free time I enjoy
sporting, reading books, and going crazy for travelling and food.
\stopblockquote

\thinrule

\subsection[education]{Education}

\startdescription{2016-2019 (expected)}
  {\bf PhD, Management Science and Technology}; Athens University of
  Economics and Business

  {\em Thesis title: Energy and Performance Implications for Software
  Development Practices}

  {\em PhD advisors:
  \useURL[url1][https://www2.dmst.aueb.gr/dds/][][Prof.~Diomidis
  Spinellis]\from[url1] and
  \useURL[url2][https://www.balab.aueb.gr/panos-panagiotis-louridas.html][][Prof.~Panos
  Louridas]\from[url2]}
\stopdescription

\startdescription{2013-2015}
  {\bf MSc, Pervasive Computing and Communications for Sustainable
  Development (PERCCOM)}; Erasmus Mundus Joint Master Degree

  ITMO University of Saint-Petersburg (Russia) {\em Thesis title:
  Implementating Green IT Approach for Transferring Big Data over
  Parallel Data Links};
  \useURL[url3][msc_thesis.pdf][][Thesis]\from[url3]

  Lulea University of Technology (Sweden) {\em Semester 3: Resource
  Efficient Pervasive Computing Systems and Communications}
  \useURL[url4][msc_lulea.pdf][][Degree]\from[url4]

  Lappeenranta University of Technology (Finland) {\em Semester 2: Smart
  Software and Services}
  \useURL[url5][msc_lappeenranta.pdf][][Degree]\from[url5]

  Unversity of Lorraine (France) {\em Semester 1: Sustainable Computer
  Network Engineering}
  \useURL[url6][msc_lorraine.pdf][][Degree]\from[url6]
\stopdescription

\startdescription{2008-2013}
  {\bf BSc, Networks and Systems Programming}; University of Cyprus

  {\em Thesis title: Implementation and Evaluation of the Biologically
  -- Inspired AntHocNet Routing Protocol in Sensor Network};
  \useURL[url7][bsc_thesis.pdf][][Thesis]\from[url7]
\stopdescription

\subsection[experience]{Experience}

{\bf Teaching and tutoring:}

Assisting my PhD advisor at Programming II course (Winter Semester of
2016, 2017, and 2018) at AUEB. Main responsibilities are giving tutorial
and Lab sessions, guiding students on team assignments and preparing
presentations.

Gave lectures and tutorials for 1st and 2nd Coding Boot Camp in Athens,
Greece (Oct. 2017 - May 2018)
\useURL[url8][https://github.com/codeandwork/courses][][Repository]\from[url8]

{\bf Proposals writing:}

Assisting Singular Logic's European Project Department for writing
proposals and participating in project's telco meetings.

\subsection[technical-experience]{Technical Experience}

\startdescription{{\em Knowledge}}
  {\em Programming Languages:} Bash, Java, Python, C, and C++

  {\em Tools and Practices:} GitHub (Travis CI, Coveralls,
  maven-plugins, GH-pages) Java plug-ings (Code Quality Check,
  maven-docker, JDBC, Reports, JUnit, JNI), Python (Pandas framework,
  Unit test,statistics, matplotlib, seaborn)
\stopdescription

\startdescription{{\em Projects}}
  {\em Measuring Energy Consumption:}
  \useURL[url9][https://github.com/stefanos1316/SEMTs_Comparisson][][Software]\from[url9]
  and
  \useURL[url10][https://stefanos1316.github.io/courses/tools/measuring_energy_consumption_direct_approach-p.html\#/][][Hardware]\from[url10]
  tools

  {\em Programming II website:}
  \useURL[url11][https://github.com/stefanos1316/courses][][Repository]\from[url11]

  {\em Rosetta Code Experiement:}
  \useURL[url12][https://github.com/stefanos1316/Rosetta_Code_Research_MSR][][Repository]\from[url12]

  {\em Validate Links:}
  \useURL[url13][https://github.com/stefanos1316/validateLinks][][Repository]\from[url13]
\stopdescription

\subsection[research-publications]{Research Publications}

\startitemize[packed]
\item
  Conference Papers
  \startitemize[packed]
  \item
    Stefanos Georgiou and Diomidis Spinellis. Energy-Delay Investigation
    of Remote Inter-Process Communication Technologies. In IPCCC 2018
    {[}To be submitted for review on 3rd of August 2018{]}
  \item
    Stefanos Georgiou, Maria Kechagia Panos Louridas, and Diomidis
    Spinellis. What Are Your Programming Language's Energy-Delay
    Implications? In 15th International Conference on Mining Software
    Repositories: Technical Track, MSR '18. New York, NY, USA, May 2018.
    Association for Computing Machinery.
    {[}\useURL[url14][GKLS18.pdf][][Paper]\from[url14]{]}
    {[}\useURL[url15][GKLS18.bib][][BibTex]\from[url15]{]}
    {[}\useURL[url16][https://www.slideshare.net/GeorgiouStefanos/what-are-your-programming-languages-energydelay-implications-106251480][][Presentation]\from[url16]{]}
    {[}\useURL[url17][https://github.com/stefanos1316/Rosetta_Code_Data_Set][][Data-set]\from[url17]{]}
  \item
    Stefanos Georgiou, Maria Kechagia, and Diomidis Spinellis. Analyzing
    Programming Languages' Energy Consumption: An Empirical Study. In
    PCI 2017: Proceedings of the 21st Pan-Hellenic Conference on
    Informatics, ACM International Conference Proceeding Series. ACM
    Press, September 2017.
    {[}\useURL[url18][GKS17.pdf][][Paper]\from[url18]{]}
    {[}\useURL[url19][GKS19.bib][][BibTex]\from[url19]{]}
    {[}\useURL[url20][https://www.slideshare.net/GeorgiouStefanos/programming-languages-energy-consumption-an-empirical-study][][Presentation]\from[url20]{]}
    {[}\useURL[url21][https://github.com/stefanos1316/Rosetta_Code_Data_Set][][Data-Set]\from[url21]{]}
  \stopitemize
\item
  Jounral Articles
  \startitemize[packed]
  \item
    Stefanos Georgiou, Stamatia Rizou, and Diomidis Spinellis. Software
    Development Life Cycle for Energy-Efficiency: Techniques and Tools.
    In ACM Computing Surveys {[}Going through major revision Sept.
    2018{]}
  \stopitemize
\stopitemize

\subsection[invited-talks]{Invited Talks}

\startdescription{Tutorials}
  {\em Travis CI with CV template tutorial} presented on 7th of June
  2018 at ITMO Univesity of Saint Petersburg for PERCCOM Master students
  in Saint-Petersburg, Russia.
  \useURL[url22][https://aueb-balab.github.io/courses/tools/travis_ci_cv_template-p.html\#/][][Presentation]\from[url22]
\stopdescription

\startdescription{Research}
  {\em What are your programming language's energy-delay implications?}
  presented on 12th of June 2018 at PERCCOM's Summer School in
  Lappeenranta, Finland.
  \useURL[url23][perccom_summer_school_2018.pdf][][Proof]\from[url23]
\stopdescription

GitHub Calendar
Crunching @IonicaBizau's contributions just for you.
\subsection[grands-awards-languages-and-living-abroad]{Grands, Awards,
Languages, and Living Abroad}

\startitemize[packed]
\item
  Grands and awards:
  \startitemize[packed]
  \item
    Best paper award from the 15th Annual DMST Student Conference (2018)
  \item
    Marie Skłodowska-Curie funds, SENECA (2016-2019)
  \item
    Erasmus Mundus Masters Scholarship, PERCCOM (2013-2015)
  \stopitemize
\item
  Human Languages:
  \startitemize[packed]
  \item
    Greek/Hungarian (Native speaker)
  \item
    English (Fluent speaker)
  \item
    Russian/ France (Basic knowledge)
  \stopitemize
\item
  Living Abroad:
  \startitemize[packed]
  \item
    Born in Gyula, Hungary but grown up in Nicosia, Cyprus.
  \item
    Ate baguettes and drunk wine in Lorraine, France (Fall Semester of
    2013)
  \item
    Took many sauna sessions in Lappeenranta, Finland (Spring Semester
    of 2014)
  \item
    Fished beers from ice-cold lakes in Lulea, Sweden (Fall Semeseter of
    2014)
  \item
    Drunk vodka and ate borsh in Saint-Petersburg, Russia (Spring
    Semester of 2015)
  \item
    Teaching in Athens and visiting islands in Greece (Fall Semester of
    2016 till now)
  \item
    Visited Delft, the Netherlands for my PhD secondment (Half month of
    Sept. 2017)
  \stopitemize
\stopitemize

\thinrule

\startblockquote
\crlf
Troias 2, ground floor, Room 03 or - Axais & Troizinias, second floor -
Athens, Greece
\stopblockquote

\stoptext
